Verifying Demonstrations

### 2018-11-29 paper/verifiability-properties.tex
Minor rephrasing for security properties
harmonizing submittable

    \item\label{CountOnce} \emph{Counted only once}:
      A protester can create \emph{one and only one} pseudonym per protest 
      (\(\pid\) in \cref{DefProofShares}), this pseudonym is unique except with 
      negligible probability.
      Analogously, a witness can create \emph{one and only one} pseudonym per 
      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
      except with negligible probability.

    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.

>>>>

    \item\label{CountOnce} \emph{Counted only once}:
      A protester can create \emph{one and only one} pseudonym (\(\pid\) in 
      \cref{DefProofShares}) per protest (\(\cid\) in \cref{DefProofShares}), 
      this pseudonym is unique except with negligible probability.
      Analogously, a witness can create \emph{one and only one} pseudonym per 
      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
      except with negligible probability.

    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof 
      is designated for the particular protest.
